---
title: "RFID antennas - Panama Vampires 2024"
output: html_notebook
---


#load packages
```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(hms)
library(readxl)
library(chron)
```


# import data
# goal: pull all files in RFID Data folder into one dataframe 
```{r}
#main data 
RFID_Data <- read_excel("RFID-2024-06-10_bayano_tole_chorrera.xlsx")
View(RFID_Data)
# import bat ID/ name data 
v2022_bats <- read_excel("/Users/maydixon/GitHub/Vamp_2023/2022_vampire_data.xlsx", sheet = "bats")
head(v2022_bats)
```

# RFID data formatting 
```{r}
#remove spaces from column names
colnames(RFID_Data) <- gsub(" ", "_", colnames(RFID_Data))

#rename S/N
RFID_Data<- rename(RFID_Data, S_N = `S/N`)


#keep only last 2 digits of Antenna_ID (delete first 0)
RFID_Data$Antenna_ID <- str_sub(RFID_Data$Antenna_ID, -2)



# make  variable with group names of each antenna (works until different groups share machines, then will have to do it by group_AntennaID)
RFID_Data <- 
      RFID_Data %>%
      mutate( Room =  recode(
      S_N,
      "1625" = "C",
      "1436" ="T",
      "1624" = "B")
            )


#c make room_AntennaID dummy variable with antenna number and group/room
RFID_Data <- 
      RFID_Data %>%
      mutate(Room_AntennaID = paste(Room,  Antenna_ID, sep = ""))
    
#format dates and times 

#Scan date as date
RFID_Data$Scan_Date<- as.Date(RFID_Data$Scan_Date, format = "%m/%d/%Y", tz= "America/Panama")

#Scan Date_Time as date_time
RFID_Data  <- RFID_Data %>%
      mutate(Scan_DateTime = paste(Scan_Date, Scan_Time, sep = " ")) %>%
      mutate(Scan_DateTime = as.POSIXct(Scan_DateTime, tz= "America/Panama")) %>%
      relocate(Scan_Date, Scan_Time, Scan_DateTime)

#Read Scan_Time as HMS
RFID_Data$Scan_Time <- as_hms(RFID_Data$Scan_Time)


#make a "night of Date" function, where midnight to 11:59am the next day are given the date of the previous day, to seperate data into nights
 RFID_Data <- 
       RFID_Data %>%
      mutate(Night_of_Date = as.Date(ifelse(Scan_Time > 12, Scan_Date, Scan_Date-1))) %>%
       relocate(Scan_Date, Night_of_Date)

#make hms(), then make it a factor ordered 12-


# add antenna types
 #add coordinates
 # add unique locations (combine ones that are the same really)
RFID_Data <- 
      RFID_Data %>%
      mutate( Locations =  recode(
      Room_AntennaID,
      "C08" = "C07",
      "C10" = "C09",
      "C12" = "C11",
      "T11" = "T10",
      "T13" = "T12",
      "B10" = "B09",
      "B08" = "B07")
            ) %>%
      mutate(Locations = recode(
           Locations, #change  door names 
          "B11" = "CBDoor", 
          "B12" = "BCDoor",
          "B13" = "BTDoor",
          "B14" = "TBDoor")) %>%
          
      mutate(Antenna_Type = case_match(
           Room_AntennaID, #add antenna types
          "C01" ~ "Large", 
          "C02" ~ "Large",
          "C03" ~ "Large", 
          "C04" ~ "Large",
          "C05" ~ "Large", 
          "C06" ~ "Large",
          "C07" ~ "Small", 
          "C08" ~ "Flat",
          "C09" ~ "Small", 
          "C10" ~ "Flat", 
          "C11" ~ "Small", 
          "C12" ~ "Flat",
          "C13" ~ "Small",
          c("T01", "T02", "T03", "T04", "T05", "T06") ~ "Large", 
          c("T07", "T08", "T09", "T10", "T12") ~ "Small", 
          c("T11", "T13") ~ "Flat", 
          c("B01", "B02", "B03", "B04", "B05", "B06") ~ "Large",
          c("B07", "B09") ~ "Small", 
          c("B08", "B10") ~ "Flat", 
          c("C14", "C15", "C16","T14", "T15", "T16","B14", "B15", "B16") ~ "Feeder", 
          c("CBDoor","BCDoor","BTDoor", "TBDoor") ~ "Door"
          )
      ) %>%
      mutate(Coords = case_match(
           Locations, # add coordinates, start with "X,Y", and then split into two columns with "," as seperateor 
          "C01" ~ "20,200", 
          "C02" ~ "155,200",
          "C03" ~ "20,125", 
          "C04" ~ "150, 125",
          "C05" ~ "20, 45", 
          "C06" ~ "150, 38",
          "C07" ~ "15,8", 
          "C09" ~ "74,8", 
          "C11" ~ "160,8", 
          "C13" ~ "164,160",
          "C14" ~  "58,146",
          "C15" ~  "83,146",
          "C16" ~  "108,146",
          "CTDoor" ~ "175,93",
          "TCDoor" ~ "180,93",
           "T01" ~ "200,200", 
          "T02" ~ "326,200",
          "T03" ~ "200,125", 
          "T04" ~ "326, 125",
          "T05" ~ "200,45", 
          "T06" ~ "326,45",
          "T07" ~ "187,169", 
          "T08" ~ "189,75",
          "T09" ~ "195,8", 
          "T10" ~ "246,8", 
          "T12" ~ "336,8",
          "T13" ~ "Small",
          "T14" ~ "240,146",
          "T15" ~  "264,146",
          "T16" ~  "292,146",
          "TBDoor" ~ "348,93",
          "BTDoor" ~ "353,93",
          "B01" ~ "373,200", 
          "B02" ~ "453,200",
          "B03" ~ "373, 120", 
          "B04" ~ "453,100",
          "B05" ~ "373,40", 
          "B06" ~ "453,40",
          "B07" ~ "468,66", 
          "B09" ~ "458,8", 
          "B15" ~  "400,146",
          "B16" ~  "410,146"
          )) %>%
      separate_wider_delim( 
            Coords,
            delim = ",", 
            names = c("Coord_X", "Coord_Y")
                            ) %>%
      mutate_at(vars(Coord_X, Coord_Y), as.numeric)




set.seed(1)
slice_sample(RFID_Data, n = 10)




```

# script for adding vamp names to dataset
```{r}
#table with just the various bat names (also adding OG group)
v2022_names <- v2022_bats %>% select(bat_name, formal_ID, new_formal_ID, RFID_number, group_ID )


# rename to human readable names with year and groupID


      # add 22 (capture year) and group to names (e.g. bea22)
v2022_names <- v2022_names %>% mutate(bat_name_full = paste(paste0(bat_name, "22"), group_ID, sep = "_"))

#make long version of names by the names I want 
nameslong <- v2022_names %>%
  gather(ID_type, IDS, c(bat_name, formal_ID, new_formal_ID, RFID_number), na.rm = TRUE) %>%
  arrange(bat_name_full) %>%
  select( - ID_type, -group_ID)      #delete extra columns
      
nameslong

#join to database by ID, separate name and group of origin
RFID_Data <- RFID_Data %>%
  left_join(nameslong, by = c("DEC_Tag_ID" = "IDS")) %>%
      separate_wider_delim(bat_name_full, delim = "_", names = c("Bat_ID", "Bat_Group"))
 

   
head(RFID_Data)
    


```

# Explore antenna locations
```{r}
RFID_Data %>%
      ggplot(aes(x= Coord_X, y=Coord_Y, color = HEX_Tag_ID)) +
      geom_jitter(alpha = 0.5) +
      scale_y_reverse() + #limits = c(228,0)
      theme_dark()+
       theme(legend.position = "none")   +
      geom_vline(xintercept = 178 ) +
      geom_vline(xintercept = 178+173+3 ) 
      
```



# explore data structure
```{r}
str(RFID_Data)
```

# explore data
```{r}
#Number of reads in each group
RFID_Data %>%
      group_by(Room) %>%
      summarise(n=n())

#Dates in the data
RFID_Data %>%
      group_by(RFID_Data$Night_of_Date) %>%
      summarise(n=n())

```
# make labelling function to plot with midnight in the middle
# stackoverflow solution from Allan Cameron: https://stackoverflow.com/questions/68578242/plot-arrival-and-departure-times-that-cross-midnight
```{r}
# R: split days at noon? 


# The hms format stores time as seconds internally.
# There are 86400 seconds in 24 hours and 43200 seconds in 12 hours, so our
# labelling function adds 43200 seconds to increase the time values by 12
# hours, then gives the result modulo 86400 to deal with values above 24 hours.
# The result is an integer number of seconds, so we need to convert this with as_hms.
# Finally we take the first 5 characters of the result with substr to give %H:%M
# formatted character strings as the labels

labelling_fn <- function(x) {
  (as.numeric(x + 43200) %% 86400) %>%
     as_hms()                      %>%
     substr(1, 5)
}

#Now pass the labelling function to the labels argument of scale_x_time
# doesn't work at the moment, except for centering axis. But not sure how to shift date-Time. 
RFID_Data %>%
      filter(Room == "C") %>%
      filter(Night_of_Date == "2024-05-13" ) %>%
      filter(Antenna_ID == c("14", "15", "16")) %>%
ggplot(aes(y = Bat_ID, x = as_hms((Scan_Time-hours(12))), color = Antenna_ID)) + #as_hms(Scan_Time-hours(12))
  geom_point() +
  scale_x_time(labels = labelling_fn) +
  labs(x = "Feed Time",
       y = "Bat ID")
```


#when are bats visiting all the feeders?
```{r}
RFID_Data %>%
      filter(Room == "T") %>% #tole is selected
      filter(Night_of_Date == "2024-05-13") %>%
     # filter(Antenna_ID == c("14", "15", "16")) %>%
      ggplot(aes(y=Antenna_ID,
                 x= Scan_Time,
                 colour = DEC_Tag_ID)) +
       geom_point( alpha = 0.1) +
      theme(axis.text.x = element_text(angle = 45)) 

```

#who is feeding at the feeders and when? 
#select one reader (S_N)
```{r}
RFID_Data %>%
      filter(S_N == "1436") %>% #tole is selected
      filter(Scan_Date == "2024-05-13") %>%
      filter(Antenna_ID == c("14", "15", "16")) %>%
      ggplot(aes(y=Antenna_ID,
                 x= Scan_Time,
                 colour = DEC_Tag_ID)) +
       geom_point( alpha = 0.1) +
      theme(axis.text.x = element_text(angle = 45)) 


RFID_Data %>%
      filter(Room == "T") %>%
      filter(Scan_Date == "2024-05-15") %>%
      filter(Antenna_ID == c("14", "15", "16")) %>%
      ggplot(aes(y=DEC_Tag_ID,
                 x= Scan_Time,
                 colour = Antenna_ID)) +
      geom_point( alpha = 0.1) +
      theme(axis.text.x = element_text(angle = 45))   #

```


# make column for "unique" antenna locations
# in progress
```{r}
unique(RFID_Data$Group_AntennaID)
# RFID_Data <- 
#       RFID_Data %>%
#       mutate( unique_loc =  recode(
#       Group_AntennaID,
#       "C_09" = "C_08",
#       "1436" ="T",
#       "1624" = "B")
#             )


```



