---
title: "RFID antennas - Panama Vampires 2024"
output: html_notebook
---


#load packages
```{r}
library(tidyverse)
library(readr)
library(lubridate)
library(hms)
library(readxl)
library(chron)
library(Hmisc)
```

# https://dshizuka.github.io/networkanalysis/networktypes_socialnetworks.html

# import data
# goal: pull all files in RFID Data folder into one dataframe 
```{r}

# import bat ID/ name data 
v2022_bats <- read_excel("/Users/maydixon/GitHub/Vamp_2023/2022_vampire_data.xlsx", sheet = "bats")
head(v2022_bats)

#main data 
#RFID_Data <- read_excel("RFID-2024-06-10_bayano_tole_chorrera.xlsx")
#View(RFID_Data)

# import  data- take all the files in a folder and pull them into the same dataframe

RFID_Data_full <- list.files(path = "Raw Data/",  # Identify all excl files with RFID in the name
                       pattern = "RFID", full.names = TRUE) %>% #
  lapply(read_excel) %>%  # Store all files in list
  bind_rows     # Combine data sets into one data set 

head(RFID_Data_full)
write.csv(RFID_Data_full, "RFID_Data.CSV")

str(RFID_Data_full)

RFID_Data <- RFID_Data_full
#View bit of  code to see if okay
# set.seed(1)
# test_data <- slice_sample(RFID_Data_full, n = 10000) # to run with a smaller set
# RFID_Data <- test_data
```

# RFID data shaping 
```{r}
#filter out duplicate rows
nrow(RFID_Data)

RFID_Data <-RFID_Data %>%
  distinct(.keep_all = TRUE)

nrow(RFID_Data)
```


```{r}
#remove spaces from column names
colnames(RFID_Data) <- gsub(" ", "_", colnames(RFID_Data))

#rename S/N
RFID_Data<- rename(RFID_Data, S_N = `S/N`)


#keep only last 2 digits of Antenna_ID (delete first 0)
RFID_Data$Antenna_ID <- str_sub(RFID_Data$Antenna_ID, -2)



# make  variable with group names of each antenna (works until different groups share machines, then will have to do it by group_AntennaID)
RFID_Data <- 
      RFID_Data %>%
      mutate( Room =  recode(
      S_N,
      "1625" = "C",
      "1436" ="T",
      "1624" = "B")
            )


#c make room_AntennaID dummy variable with antenna number and group/room
RFID_Data <- 
      RFID_Data %>%
      mutate(Room_AntennaID = paste(Room,  Antenna_ID, sep = ""))
    
#format dates and times 

#Scan date as date
RFID_Data$Scan_Date<- as.Date(RFID_Data$Scan_Date, format = "%m/%d/%Y", tz= "America/Panama")

#Scan Date_Time as date_time
RFID_Data  <- RFID_Data %>%
      mutate(Scan_DateTime = paste(Scan_Date, Scan_Time, sep = " ")) %>%
      mutate(Scan_DateTime = as.POSIXct(Scan_DateTime, tz= "America/Panama")) %>%
      relocate(Scan_Date, Scan_Time, Scan_DateTime)

#Read Scan_Time as HMS
RFID_Data$Scan_Time <- as_hms(RFID_Data$Scan_Time)


#make a "night of Date" function, where midnight to 11:59am the next day are given the date of the previous day, to seperate data into nights
 RFID_Data <- 
       RFID_Data %>%
      mutate(Night_of_Date = as.Date(ifelse(Scan_Time > 12, Scan_Date, Scan_Date-1))) %>%
       relocate(Scan_Date, Night_of_Date)

#make hms(), then make it a factor ordered 12-


# add antenna types
 #add coordinates
 # add unique locations (combine ones that are the same really)
RFID_Data <- 
      RFID_Data %>%
      mutate( Locations =  recode(
      Room_AntennaID,
      "C08" = "C07",
      "C10" = "C09",
      "C12" = "C11",
      "T11" = "T10",
      "T13" = "T12",
      "B10" = "B09",
      "B08" = "B07")
            ) %>%
      mutate(Locations = recode(
           Locations, #change  door names 
          "B11" = "CTDoor", 
          "B12" = "TCDoor",
          "B13" = "BTDoor",
          "B14" = "TBDoor")) %>%
          
      mutate(Antenna_Type = case_match(
           Room_AntennaID, #add antenna types
          "C01" ~ "Large", 
          "C02" ~ "Large",
          "C03" ~ "Large", 
          "C04" ~ "Large",
          "C05" ~ "Large", 
          "C06" ~ "Large",
          "C07" ~ "Small", 
          "C08" ~ "Flat",
          "C09" ~ "Small", 
          "C10" ~ "Flat", 
          "C11" ~ "Small", 
          "C12" ~ "Flat",
          "C13" ~ "Small",
          c("T01", "T02", "T03", "T04", "T05", "T06") ~ "Large", 
          c("T07", "T08", "T09", "T10", "T12") ~ "Small", 
          c("T11", "T13") ~ "Flat", 
          c("B01", "B02", "B03", "B04", "B05", "B06") ~ "Large",
          c("B07", "B09") ~ "Small", 
          c("B08", "B10") ~ "Flat", 
          c("C14", "C15", "C16","T14", "T15", "T16","B14", "B15", "B16") ~ "Feeder", 
          c("B11","B12","B13", "B14") ~ "Door"
          )
      ) %>%
      mutate(Coords = case_match(
           Locations, # add coordinates, start with "X,Y", and then split into two columns with "," as separator 
          "C01" ~ "20,200", 
          "C02" ~ "155,200",
          "C03" ~ "20,125", 
          "C04" ~ "150, 125",
          "C05" ~ "20, 45", 
          "C06" ~ "150, 38",
          "C07" ~ "15,8", 
          "C09" ~ "74,8", 
          "C11" ~ "160,8", 
          "C13" ~ "164,160",
          "C14" ~  "58,146",
          "C15" ~  "83,146",
          "C16" ~  "108,146",
          "CTDoor" ~ "175,93",
          "TCDoor" ~ "180,93",
           "T01" ~ "200,200", 
          "T02" ~ "326,200",
          "T03" ~ "200,125", 
          "T04" ~ "326, 125",
          "T05" ~ "200,45", 
          "T06" ~ "326,45",
          "T07" ~ "187,169", 
          "T08" ~ "189,75",
          "T09" ~ "195,8", 
          "T10" ~ "246,8", 
          "T12" ~ "336,8",
          "T13" ~ "Small",
          "T14" ~ "240,146",
          "T15" ~  "264,146",
          "T16" ~  "292,146",
          "TBDoor" ~ "348,93",
          "BTDoor" ~ "353,93",
          "B01" ~ "373,200", 
          "B02" ~ "453,200",
          "B03" ~ "373, 120", 
          "B04" ~ "453,100",
          "B05" ~ "373,40", 
          "B06" ~ "453,40",
          "B07" ~ "468,66", 
          "B09" ~ "458,8", 
          "B15" ~  "400,146",
          "B16" ~  "410,146"
          )) %>%
      separate_wider_delim( 
            Coords,
            delim = ",", 
            names = c("Coord_X", "Coord_Y")
            ) %>%
      mutate_at(vars(Coord_X, Coord_Y), as.numeric)


#hmisc describe function to explore values       
describe(RFID_Data) 

# explore unique values - looking for any NAs
lapply(RFID_Data[,15:20], unique )
# all good


```

# script for adding vamp names to dataset
```{r}

#remove period from decimal bat name to make it match vamp name list
RFID_Data$DEC_Tag_ID <- RFID_Data$DEC_Tag_ID %>%
      str_remove( "[.]") 


#table with just the various bat names (also adding OG group)
v2022_names <- v2022_bats %>% select(bat_name, formal_ID, new_formal_ID, RFID_number, group_ID )


# rename to human readable names with year and groupID


      # add 22 (capture year) and group to names (e.g. bea22)
v2022_names <- v2022_names %>% mutate(bat_name_full = paste(paste0(bat_name, "22"), group_ID, sep = "_"))

#make long version of names by the names I want 
nameslong <- v2022_names %>%
  gather(ID_type, IDS, c(bat_name, formal_ID, new_formal_ID, RFID_number), na.rm = TRUE) %>%
  arrange(bat_name_full) %>%
  select( - ID_type, -group_ID)      #delete extra columns

# add test tag to dataset (remove later)      
nameslong <- nameslong %>%rbind(c("test_NA", 989001040984122))

#join to database by ID, separate name and group of origin
RFID_Data <- RFID_Data %>%
  left_join(nameslong, by = c("DEC_Tag_ID" = "IDS")) %>%
      separate_wider_delim(bat_name_full, delim = "_", names = c("Bat_ID", "Bat_Group"))
 

#############
#troubleshoot, which names aren't coming through? 
#pull all names that are coming through
 RFID_Data %>%
       group_by(Bat_ID)%>%
      arrange(Bat_ID) %>%
      slice_head(n = 1) %>%
       select(Bat_ID) 

v2022_names %>%arrange(bat_name)
#no kamari: 9890010404606665

 RFID_Data %>%
       filter(is.na(Bat_ID)) %>% nrow()
 
 RFID_Data %>%
       filter(is.na(Bat_ID)) %>%
       group_by(DEC_Tag_ID) %>%
       slice_head(n = 1) 

 #get rid of strange values (interference? To only have known bats (get rid of test tags as well))
 
RFID_Data <-  RFID_Data %>%
       filter(!is.na(Bat_ID))

###########################
head(RFID_Data)

 #writecombined data   
write.csv(RFID_Data, "Combined_Data/RFID_Data.CSV", row.names = F) 
#
test_data <- slice_sample(RFID_Data, n = 10000) # to run with a smaller set
test_data2 <- head(RFID_Data, 10000) #data with continuous runs
```

# Try to convert data into durations
# Adapted from Jay Falk code "Collapse Duration"
This function uses data made from the readin.RFID function and collapses it so that it shows the number of seconds present at a feeder and at what time. It also takes into account when a bird leaves the feeder for a short amount of time and comes back, and will collapse these together. The secaway variable is the amount of time away from the feeder that the function will allow the bird to leave the feeder before it considers it a new feed
```{r}
test_data2 %>%
      arrange(Locations, Scan_DateTime)
```

```{r duration-function}

#Could start here, with loaded RFID data 

duration.RFID <- function(datafile, secaway){ #This function uses a data made from readin.RFID function and collapses it so that it shows the number of seconds present at an antenna and at what time
  datafile <- datafile %>% arrange(Locations, Scan_DateTime) #possibly should use another feeder
  collapsed <- tibble() #creates a new tibble to be returned 
  templine <- tibble(rawtext = "x", RFID = "x", id = "x", stringtime = "1999-01-01 00:00:00", time = "1999-01-01 00:00:00", station = "x") #creates a temporary junk line to the end so that the conditional statements work for the last line of data
  datafile <- rbind(datafile, templine) #adds the junk line to the end of the data file
  count <- dseconds(1) #count holds the number of seconds present at the feeder, including any gaps less than or equal to secaway
  feedsecs <- 1 #feedsecs holds the number of seconds actually feeding, NOT incuding the secaway gaps
  secs <- as.duration(secaway)
  for(i in 1:(nrow(datafile)-1)) {
    if(((datafile$time[i+1] - datafile$time[i]) <= secs) && 
       (datafile$id[i+1] == datafile$id[i]) &&
       (datafile$station[i+1] == datafile$station[i])){#checks if the time in line i is only one second lower than the line after i, and if it's the same bird
      count <- count + as.duration(datafile$time[i+1] - datafile$time[i]) #if the above statement is true, this continues to grow until there is a break in the continuity of the feed
      feedsecs <- feedsecs + 1
    }
    else {#if the seconds are not continuous, this creates a new line to be added to the "collapsed" tibble with all the necessary info
      templine <- tibble(
        id = datafile$id[i],
        starttime = datafile$time[i] - dseconds(count-1),
        station = datafile$station[i],
        duration = count,
        feeding = as.duration(feedsecs)
      )
      collapsed <- rbind(collapsed, templine) #combines the newest line of collapsed data to the other lines
      count <- 1 #returns the duration count to 1 to start over at the top of the for loop
      feedsecs <- 1 #returns the time feeding to 1 to start over at the top of the for loop
    }
  }
  return(collapsed)
}
```
```{r}

```









# Explore antenna locations
```{r}
RFID_Data %>%
      ggplot(aes(x= Coord_X, y=Coord_Y, color = Antenna_Type)) +
      geom_jitter(alpha = 0.5) +
      scale_y_reverse() + #limits = c(228,0)
      theme_dark()+
       theme(legend.position = "none")   +
      geom_vline(xintercept = 178 ) +
      geom_vline(xintercept = 178+173+3 ) 
      
```



# explore data structure
```{r}
str(RFID_Data)
```

# explore data
```{r}
#Number of reads in each group
RFID_Data %>%
      group_by(Room) %>%
      summarise(n=n())

#Dates in the data
RFID_Data %>%
      group_by(RFID_Data$Night_of_Date) %>%
      summarise(n=n())

```
# make labelling function to plot with midnight in the middle
# stackoverflow solution from Allan Cameron: https://stackoverflow.com/questions/68578242/plot-arrival-and-departure-times-that-cross-midnight
```{r}
# R: split days at noon? 


# The hms format stores time as seconds internally.
# There are 86400 seconds in 24 hours and 43200 seconds in 12 hours, so our
# labelling function adds 43200 seconds to increase the time values by 12
# hours, then gives the result modulo 86400 to deal with values above 24 hours.
# The result is an integer number of seconds, so we need to convert this with as_hms.
# Finally we take the first 5 characters of the result with substr to give %H:%M
# formatted character strings as the labels

labelling_fn <- function(x) {
  (as.numeric(x + 43200) %% 86400) %>%
     as_hms()                      %>%
     substr(1, 5)
}

#Now pass the labelling function to the labels argument of scale_x_time
# doesn't work at the moment, except for centering axis. But not sure how to shift date-Time. 
RFID_Data %>%
      filter(Room == "C") %>%
      filter(Night_of_Date == "2024-05-13" ) %>%
      filter(Antenna_ID == c("14", "15", "16")) %>%
ggplot(aes(y = Bat_ID, x = as_hms((Scan_Time-hours(12))), color = Antenna_ID)) + #as_hms(Scan_Time-hours(12))
  geom_point() +
  scale_x_time(labels = labelling_fn) +
  labs(x = "Feed Time",
       y = "Bat ID")
```


#when are bats visiting all the feeders?
```{r}
RFID_Data %>%
      filter(Room == "T") %>% #tole is selected
      filter(Night_of_Date == "2024-05-13") %>%
     # filter(Antenna_ID == c("14", "15", "16")) %>%
      ggplot(aes(y=Antenna_ID,
                 x= Scan_Time,
                 colour = DEC_Tag_ID)) +
       geom_point( alpha = 0.1) +
      theme(axis.text.x = element_text(angle = 45)) 

```

#who is feeding at the feeders and when? 
#select one reader (S_N)
```{r}
RFID_Data %>%
      filter(S_N == "1436") %>% #tole is selected
      filter(Scan_Date == "2024-05-13") %>%
      filter(Antenna_ID == c("14", "15", "16")) %>%
      ggplot(aes(y=Antenna_ID,
                 x= Scan_Time,
                 colour = DEC_Tag_ID)) +
       geom_point( alpha = 0.1) +
      theme(axis.text.x = element_text(angle = 45)) 


RFID_Data %>%
      filter(Room == "T") %>%
      filter(Scan_Date == "2024-05-15") %>%
      filter(Antenna_ID == c("14", "15", "16")) %>%
      ggplot(aes(y=DEC_Tag_ID,
                 x= Scan_Time,
                 colour = Antenna_ID)) +
      geom_point( alpha = 0.1) +
      theme(axis.text.x = element_text(angle = 45))   #

```


# make column for "unique" antenna locations
# in progress
```{r}
unique(RFID_Data$Group_AntennaID)
# RFID_Data <- 
#       RFID_Data %>%
#       mutate( unique_loc =  recode(
#       Group_AntennaID,
#       "C_09" = "C_08",
#       "1436" ="T",
#       "1624" = "B")
#             )


```



